### 2020-06-23 Documents/ESA/sections/Intro.tex
Updated ESA

    Swarm robotics bases its success upon the collaboration of many agents who contribute towards
    the overall success of the system \cite{HammanFormalApproach}. The collaboration of many agents
    who share the same goal can give rise to behaviours that are far more complex than individual
    robots can achieve. The capacity for complexity is becoming increasingly important as robots are
    we are presented with ever more challenging tasks including: search and rescue, cleaning up
    space debris, and robotic assembly. Such tasks are beyond the capabilities of individual robots
    and so we must leverage the capacity for agents in a swarm to collectively achieve our
    goals. Fortunately, a growing subset of the Control Theory community have turned their attention
    towards this very problem and address the question: how does the dynamical behaviour of a
    population of agents change under the influence of control? Note that we use the term 'agent'
    loosely here, an agent can refer to anything from a simple particle \cite{BorziCollectiveMotion}
    to a complex robot \cite{ElamvazuthisThesis}. In answering this question, researchers have
    gained a stronger understanding of how a swarm may be controlled to achieve desired results.

    Another technique which has made incredible strides towards improving the capability of
    autonomous systems to communally achieve results is Multi-Agent Reinforcement Learning (MARL)
    \cite{Schwarz}. This builds on the ideas of classical Reinforcement Learning which allows an
    agent to optimise its strategies towards tackling a task through repeated exposure to that task.
    MARL utilises this same principle with the caveat that agents must adapt their strategies based
    not only on the outcome of the action, but also on the actions of the other agents. This has
    shown strong results in practical applications \textbf{APPLICATIONREFERENCES}. Whilst MARL was
    once considered to be non-identifiable (there is no clear way of identifying the algorithm that
    a particular agent was trained on) and black box (there is no clear way of ensuring a desired
    result from a learning algorithm), a steady stream of research is emerging to lift this fog
    \cite{TuylsSurvey}. This allows for researchers to choose the parameters of their learning
    algorithms appropriately to ensure that learning agents behave in the desired manner.

@@

    \textbf{Need to talk about the scope of the project: what assumptions will be made to ensure
    that the above can be achieved within the given time constraints?}

    \section{Methodology} \label{sec::Methodology}

>>>>

    Swarm robotics bases its success upon the collaboration of many agents who contribute towards
    the overall success of the system \cite{Hamann2018}. The collaboration of many agents
    who share the same goal can give rise to behaviours that are far more complex than individual
    robots can achieve. The capacity for complexity is becoming increasingly important as robots are
    we are presented with ever more challenging tasks including: search and rescue, cleaning up
    space debris, and robotic assembly. Such tasks are beyond the capabilities of individual robots
    and so we must leverage the capacity for agents in a swarm to collectively achieve our
    goals. Fortunately, a growing subset of the Control Theory community have turned their attention
    towards this very problem and address the question: how does the dynamical behaviour of a
    population of agents change under the influence of control? Note that we use the term 'agent'
    loosely here, an agent can refer to anything from a simple particle \cite{Roy2017}
    to a complex robot \cite{Elamvazhuthi2019}. In answering this question, researchers have
    gained a stronger understanding of how a swarm may be controlled to achieve desired results.

    Another technique which has made incredible strides towards improving the capability of
    autonomous systems to communally achieve results is Multi-Agent Reinforcement Learning (MARL)
    \cite{SchwartzMulti-agentApproach}. This builds on the ideas of classical Reinforcement Learning which allows an
    agent to optimise its strategies towards tackling a task through repeated exposure to that task.
    MARL utilises this same principle with the caveat that agents must adapt their strategies based
    not only on the outcome of the action, but also on the actions of the other agents. This has
    shown strong results in practical applications \cite{Woolridge2009, SchwartzMulti-agentApproach, Yang2004}. Whilst MARL was
    once considered to be non-identifiable (there is no clear way of identifying the algorithm that
    a particular agent was trained on) and black box (there is no clear way of ensuring a desired
    result from a learning algorithm), a steady stream of research is emerging to lift this fog
    \cite{Bloembergen2015}. This allows for researchers to choose the parameters of their learning
    algorithms appropriately to ensure that learning agents behave in the desired manner.

@@

    % \section{Methodology} \label{sec::Methodology}

### 2020-06-23 Documents/ESA/sections/LitReview.tex
Updated ESA

\textbf{TODO: Elaborate on each of the metrics}

@@

POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an optimal solution is found by
fixing the strategy (a manner of selecting an action \cite{Rizk2018DecisionSurvey}) of all agents
except one. The optimal strategy of the chosen agent is then computed. This is fixed so that the
next agent may determine its optimal strategy. This process is iterated over all agents in a process
known as Alternating Maximisation \cite{Ray2010AnCooperation}. By choosing strategies which maximise
a common payoff, a globally optimal solution can be found.

Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is
sometimes referred to as an ‘incomplete information game’). This allows for a POSG to be
approximated by a sequence of smaller, more tractable games
\cite{Emery-MontemerloApproximatePayoffs}. However, iterating through the entire team of agents to
find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic
situations. To address this, \cite{Ray2010AnCooperation} propose to place distinct payoffs on each
agent and to consider team formation based on social hierarchy as well as preferred partners. This
allows the complexity of the problem to be broken down into smaller game units and also provides a
clear order in which the games are to be played. This minimises the interference across robots and
allows for more immediate action to be taken by agents who choose their strategy early on, while
leaving more passive tasks for those later in the sequence.

The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
dynamic decision making. However, as found by Dai et. al \cite{Dai2018TaskSystems} this is
conditional on an understanding by each robot of the strategy of others, which in turn requires
adequate communication between robots. Therefore, the game theoretical formulation will fail where
communication is not possible amongst team members. However, the addition of heuristics, such as
deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other
members of its team without the need for significant explicit communication.

\textbf{Add in any recent literature in these fields}

@@

The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
method of linear programming (in which constraints are linear). This will be important in
considering more current methods. A similar consideration is given to the infinitesimal gradient
ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
particular problem in games where there are multiple Nash equilibria. However, in practice it is
difficult to choose a convergence rate of the step size and, without an appropriate choice the
strategy may oscillate as shown in the book. To address this, a modified approach is presented by
Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA.
WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
payoff matrix (which is not so much of a problem for model based methods) and the opponent's
strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
players with minimal oscillation.

@@

\textbf{Add in more recent literature r.e. learning in stochastic games and the robustness of MARL}

@@

\textbf{Include recent updates in here}

@@

\textbf{Include Marco Dorigo and Recent AAMAS literature in here}

@@

\textbf{TODO: Go through each of the sections and explicitly evaluate them against the defined
metrics}

>>>>

@@

POSGs act as a game theoretic corollary to the Dec-POMDP. Here, an optimal solution is found by
fixing the strategy (a manner of selecting an action \cite{Rizk2018}) of all agents
except one. The optimal strategy of the chosen agent is then computed. This is fixed so that the
next agent may determine its optimal strategy. This process is iterated over all agents in a process
known as Alternating Maximisation \cite{Ray2010}. By choosing strategies which maximise
a common payoff, a globally optimal solution can be found.

Similarly Bayesian Games is a game theoretic approach with incomplete information (thus it is
sometimes referred to as an ‘incomplete information game’). This allows for a POSG to be
approximated by a sequence of smaller, more tractable games
\cite{Emery-Montemerlo}. However, iterating through the entire team of agents to
find an optimal solution is a lengthy process and does not allow for immediate actions in dynamic
situations. To address this, \cite{Ray2010} propose to place distinct payoffs on each
agent and to consider team formation based on social hierarchy as well as preferred partners. This
allows the complexity of the problem to be broken down into smaller game units and also provides a
clear order in which the games are to be played. This minimises the interference across robots and
allows for more immediate action to be taken by agents who choose their strategy early on, while
leaving more passive tasks for those later in the sequence.

The Bayesian Game formulation therefore provides a strong candidate for rapid task re-allocation and
dynamic decision making. However, as found by Dai et. al \cite{Dai2018} this is
conditional on an understanding by each robot of the strategy of others, which in turn requires
adequate communication between robots. Therefore, the game theoretical formulation will fail where
communication is not possible amongst team members. However, the addition of heuristics, such as
deep learning, may be able to advance an agent’s ability to recognise the strategies taken by other
members of its team without the need for significant explicit communication.

% \textbf{Add in any recent literature in these fields}

@@

The most fundamental method to learning in Matrix games is the simplex algorithm. This is a popular
method of linear programming (in which constraints are linear). This will be important in
considering more current methods. A similar consideration is given to the infinitesimal gradient
ascent algorithm, in which the step size converges to zero. This method guarantees that, in the
infite horizon limit, the payoffs will converge to the Nash equilibrium payoff. Note that this does
not necessarily mean that both agents will converge to a single Nash equilibrium. This is a
particular problem in games where there are multiple Nash equilibria. However, in practice it is
difficult to choose a convergence rate of the step size and, without an appropriate choice the
strategy may oscillate as shown in the book. To address this, a modified approach is presented by
Bowling and Veloso which incorporates the notion of Win or Learn Fast (WoLF) to produce WoLF-IGA
\cite{Bowling2002}.
WoLF is a notion we will come across often in MARL and is shown by the authors to converge to always
to a NE. The concern with WoLF methods, however, is that it requires explicit knowledge of the
payoff matrix (which is not so much of a problem for model based methods) and the opponent's
strategy (which is more of a problem in real-world methods). Finally, the Policy Hill Climbing
method (PHC) is shown to converge to an optimal mixed strategy if the other agents are stationary
(i.e. are not learning). However, it is shown that, when this is not the case, the algorithm again
oscillates. The WoLF-PHC adaptation of this method is shown to converge to a NE strategy for both
players with minimal oscillation.

@@

% \textbf{Add in more recent literature r.e. learning in stochastic games and the robustness of
% MARL}

@@

% \textbf{Include recent updates in here}

@@

% \textbf{Include Marco Dorigo and Recent AAMAS literature in here}

@@

### 2020-06-23 Documents/ESA/sections/ProposedResearch.tex
Updated ESA

	\textbf{TODO: Ensure all references here are in the Lit Review}

@@

    It has long been established that, upon lifting the strong assumptions made by traditional
    game theory (such as the rationality of agents and complete information), that player
    strategies can result in much more complex behaviour than convergence to a Nash Equilibrium 
    (NE). In fact, this is even true on what would commonly be regarded as 'simple' games such
    as tic-tac-toe and prisoner's dilemma \cite{Galla's work and I think Sato's work}. These
    behaviours include: convergence to a unique equilibrium (though not always to an NE),
    convergence to one of multiple equilibria, limit cycles and chaos. These behaviours are shown in
    Figure ... Of these, the most preferable is, of course, convergence to a unique equilibrium,
    although it is still possible to study systems with multiple equilibria or limit cycles 
    \cite{One of the textbooks}. However, it would be difficult to control systems whose dynamics
    are governed by chaos (though research into controlling chaos is ongoing and rife with
    opportunity \cite{CyberneticalPhysics}) and so MARL techniques should avoid this. It would,
    therefore, be a useful endeavour to determine the conditions under which these sorts of
    behaviours arise.

@@

	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
	memory and intensity of choice parameters respectively. Agent 1 takes action i with probability
	$x_i$ while Agent 2 takes action j with probability $y_j$. If these actions are taken, the agents
	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
	predict the expected behaviour of Q-Learning agents, as shown in Figure ...

	It is clear, both from (\ref{eqn::EOM}) and Figure ... that the long-term strategy selection of
	these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
	then pose the question: how do these elements influence the types of behaviours seen during
	learning on an iterated game? In other words, under what parameter selections are we likely to
	see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?

	With this in mind, the intention of this area of study is to consider the analysis presented in
	works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
	learning behaviour of human players in a game \cite{whatevertheycite}. The authors are able to
	determine the regions of parameter space in which complex behaviour,
	including cycles and chaos, predominantly occur and those in which a given game converges to a
	stable equilibrium. Figure ... reproduces the graphs shown in \cite{Sanders2018} which
	illustrates the successful derivation of a 'phase line', across which learning shifts from
	convergent to chaotic.

@@

    This segment of research is currently underway and approaching completion. The analysis can be
    seen in Section \ref{sec::Chaos_in_Q-Learning}.

    \section{Large Agent Dynamics} \label{sec::Large_Agent_Dynamics}

@@

    One of the main results shown by Sanders et al. \cite{Sanders2018} is that as the number of
    players in a game increases, the learning behaviour is more likely to be chaotic, regardless of
    the choice of parameters. This is intuitive since a higher number of players would result in a
    greater strategy space and more agents for any particular player to learn against and is
    verified by their presented results as in Figure ...

    Yet it can be argued that, for large populations of agents (e.g. a crowd), the aggregate
    behaviour may be predictable. This intuition is the foundation upon which crowd dynamics and
    flocking systems are based. In fact, the work presented by Leung et al. \cite{Hu2019} provides a
    cursory verification of this intuition. Here, the authors present an anaysis of the learning
    dynamics for a large agent population (which they approximate as containing infinite agents)
    where each agent is an independent Q-Learning using Boltzmann action selection. The
    result is a system of equations, governed by a Fokker-Planck model which is numerical shown to be a 
    strong predictor of the overall strategy selection of the population. Indeed, rather than
    examining the strategies of every agent in the population (which the authors approximate as
    infinitely large), they model the evolution of a probability density function which, for each
    action, defines the density of agents who retain a given Q-value for that action. This is
    illustrated in Figure ...

@@

	Two proposals for how this might work

	\begin{itemize}
		\item Estimate the population state using a Random Finite Set (RFS) and apply the models
		from the previous study. This is a new hypothesis so more research is required.
		\item Decompose a generic game into a weighted sum of a competitive and a cooperative game.
		Treat these as two separate agents and invoke the mean field approximation so that any given
		agent is effectively engaged in a three-player game where the strategy of the opponents is
		the average strategy of the population.
	\end{itemize}

	\textbf{TODO: Elaborate on the technical details of the RFS and three body hypotheses}

@@

    As described in the previous chapter, the control of swarms has been examined through the use of
    mean field models. These models resolve the fact that it is impossible to view the entire system
    as simply the sum of all of the agents and rather model the overall state of the system through
    density functions. Controls are then applied to this function whose evolution is described
    through, typically, one of two partial differential equations: the Fokker-Planck Equation (also
    referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
    some success in recent literature \cite{Zhang2018, Elamvazhuthi2019, Li2017,
    BorziCollectiveMotion}, though it makes the assumption that the system evolves through 'drifted
    brownian motion'. This means that the agents are considered to move about independently and
    randomly, though under the influence of a field which affects their velocity. This technique
	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
	manner \cite{Any paper of Fokker Planck control}. The latter is beginning to show promise 
	though control is typically through leadership rather than fields \cite{VlasovMPC}.

@@

	\begin{itemize}
		\item The stablity of the system: Under what conditions is it possible to drive the
		swarm from one configuration to another in a stable manner?
		\item The guarantees of the system: Is it possible to ensure that controls remain within an
		admissible set (typically a closed, bounded and convex set \cite{PDEControl}).
	\end{itemize}

@@

	Two proposals for incorporation of social interaction:
	\begin{itemize}
		\item Addition of the agent decisions as a constant in the state $f$. This should be fine if
		it's fixed but note that the controls have no influence over this.
		\item Multiplicative term in the turning probability which acts as a weighting term where
		weights are equal to the agent strategy. This extends to both the swarms in
		which the leaders are making decisions (only leaders have this term) as well as in
		swarms where the population makes decisions (everyone has this term). This will need to be
		done with care though to ensure that normalisation holds.
	\end{itemize}

@@

	\textbf{TODO: elaborate on the technical details for proposals of social interaction, mention
	the conservation laws}

>>>>

	% \textbf{TODO: Ensure all references here are in the Lit Review}

@@

    It has long been established that, upon lifting the strong assumptions made by traditional
    game theory (such as the rationality of agents and complete information), that player
    strategies can result in much more complex behaviour than convergence to a Nash Equilibrium 
    (NE). In fact, this is even true on what would commonly be regarded as 'simple' games such
    as tic-tac-toe and prisoner's dilemma \cite{Galla2011, Sato2002}. These
    behaviours include: convergence to a unique equilibrium (though not always to an NE),
    convergence to one of multiple equilibria, limit cycles and chaos. These behaviours are shown in
    Figure \ref{fig::DynamicalBehaviours} Of these, the most preferable is, of course, convergence to a unique equilibrium,
    although it is still possible to study systems with multiple equilibria or limit cycles 
    \cite{Strogatz2000}. However, it would be difficult to control systems whose dynamics
    are governed by chaos (though research into controlling chaos is ongoing and rife with
    opportunity \cite{Fradkov2009}) and so MARL techniques should avoid this. It would,
    therefore, be a useful endeavour to determine the conditions under which these sorts of
    behaviours arise.

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=1.1\textwidth]{Figures/DynamicalBehaviours}
    	\caption{ \label{fig::DynamicalBehaviours} Different types of dynamial behaviour displayed
    	by learning agents. a)
    	Convergence
    	to a unique fixed point in the upper right corner (1, 1). This fixed point is unique, in
    	that all trajectories, regardless of initialisation, will converge to this point 
    	\cite{Tuyls2006AnGames}. b) Limit Cycle, the trajectories converge to cyclic behaviour c,
    	d) Chaotic behaviour, here small deviatons in the initial conditions can grow
    	exponentially \cite{Sanders2018}.}
    \end{figure}

@@

	Here, $\alpha$ and $\tau$ are the parameters of the agent; Sanders et al. refer to these as the
	memory and intensity of choice parameters respectively. Agent 1 takes action i with probability
	$x_i$ while Agent 2 takes action j with probability $y_j$. If these actions are taken, the agents
	receive payoff $a_{ij}$ and $b_{ji}$ respectively. With these equations, it is possible to
	predict the expected behaviour of Q-Learning agents, as shown in Figure 
	\ref{fig::TuylsExperiments}.

	\begin{figure}[h]
		\centering
		\begin{subfigure}[b]{0.9 \textwidth}
			\centering
			\includegraphics[width=0.75 \textwidth]{Figures/Dynamics}
			\caption{}
		\end{subfigure}

		\begin{subfigure}[b]{0.9 \textwidth}
			\centering
			\includegraphics[width=0.7 \textwidth]{Figures/Q-Learners}
			\caption{}
		\end{subfigure}

		\caption{ \label{fig::TuylsExperiments} Figures taken from \cite{Tuyls2006AnGames} a) Phase
		plot showing the expected behaviour of Q-Learning agents trained by iterating the
		Prisoner's Dilemma game as predicted by (\ref{eqn::EOM}). From left to right, the agents
		have parameter $\tau = 1, 2, 10$. b) Corresponding trajectories of Q-Learning agents with
		randomised initial conditions displayed through numerical simulation. It is clear that the
		trajectories in b) follow the predictions in a), after stochasticity is accounted for. }
	\end{figure}

	It is clear, both from (\ref{eqn::EOM}) and Figure \ref{fig::TuylsExperiments} that the long-term strategy selection of
	these agents is determined by the parameters $\alpha, \tau$ and the payoffs $a_{ij}, b_{ij}$. We
	then pose the question: how do these elements influence the types of behaviours seen during
	learning on an iterated game? In other words, under what parameter selections are we likely to
	see convergence to unique equilibria, multiple equilibria, limit cycles or chaos?

	With this in mind, the intention of this area of study is to consider the analysis presented in
	works such as \cite{Sanders2018} and \cite{Galla2011}. Here, the authors examine the
	Experience Weighted Attraction (EWA) algorithm, which is regarded as a strong model for the
	learning behaviour of human players in a game \cite{Camerer2009}. The authors are able to
	determine the regions of parameter space in which complex behaviour,
	including cycles and chaos, predominantly occur and those in which a given game converges to a
	stable equilibrium. Figure \ref{fig::GallaPredictions} reproduces the graphs shown in \cite{Sanders2018} which
	illustrates the successful derivation of a 'phase line', across which learning shifts from
	convergent to chaotic.

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.6\textwidth]{Figures/GallaPredictions}
    	\caption{ \label{fig::GallaPredictions} Results as produced in the supplementary material
    	of Sanders et al \cite{Sanders2018}. Here, $p$ is the number of players, $N$ is the number
    	of actions, $\Gamma$ represents the competitiveness of the game (-1 represents zero-sum, 1
    	represents shared rewards) and $\alpha$ is the memory parameter of the agent as before.
    	Here $\tau$ is held constant at 0.05 (though it is referred to as $\beta$ in the paper).
    	The black region represents where games converged to a fixed point through all simulations,
    	whilst the hotter regions represent the more complex dynamics - red shows the presence of
    	limit cycles and white regions signal the onset of chaos. The green line is a theoretical
    	estimation for the phase line which separates the convergent dynamics from complex.}
    \end{figure}

@@

    This segment of research is currently underway and approaching completion. The analysis was
    described in Section \ref{sec::Chaos_in_Q-Learning}.

    \section{Large Population Dynamics} \label{sec::Large_Agent_Dynamics}

@@

    One of the main results shown by Sanders et al. \cite{Sanders2018} is that as the number of
    players in a game increases, the learning behaviour is more likely to be chaotic, regardless of
    the choice of parameters. This is intuitive since a higher number of players would result in a
    greater strategy space and more agents for any particular player to learn against and is
    verified by their presented results as in Figure \ref{fig::GallaPrevalence} - the hotter
    regions occupy a larger area as

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.6\textwidth]{Figures/GallaPrevalence}
    	\caption{ \label{fig::GallaPrevalence} Results as produced in the supplementary material
    	of Sanders et al \cite{Sanders2018}. The same items appear here as in Figure 
    	\ref{fig::GallaPredictions}, except the value of p (number of players) increases moving
    	from top left to bottom right. It is clear that the hotter region occupies a larger region
    	of parameter space, indicating that as the bumber of players in the game increase, chaos
    	becomes more prevalent.}
    \end{figure}

    Yet it can be argued that, for large populations of agents (e.g. a crowd), the aggregate
    behaviour may be predictable. This intuition is the foundation upon which crowd dynamics and
    flocking systems are based. In fact, the work presented by Leung et al. \cite{Hu2019} provides a
    cursory verification of this intuition. Here, the authors present an anaysis of the learning
    dynamics for a large agent population (which they approximate as containing infinite agents)
    where each agent is an independent Q-Learning using Boltzmann action selection. The
    result is a system of equations, governed by a Fokker-Planck model which is numerical shown to be a 
    strong predictor of the overall strategy selection of the population. Indeed, rather than
    examining the strategies of every agent in the population (which the authors approximate as
    infinitely large), they model the evolution of a probability density function which, for each
    action, defines the density of agents who retain a given Q-value for that action. This is
    illustrated in Figure \ref{fig::LeungPredictions}.

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.9\textwidth]{Figures/LeungPredictions}
    	\caption{ \label{fig::LeungPredictions} Results as produced in Leung et al \cite{Hu2019}.
    	Here, the solid and dotted lines represent the evolution of thhe expectation of Q-values of
    	two actions across a population of 50 or 999 agents respectively who are trained on an
    	iterated Stag Hunt game. The circled and crossed
    	lines represent the dynamics of these Q-values as predicted by the system of equations
    	derived in the paper. These are seen to closely match the results of the numerical
    	experiments.}
    \end{figure}

@@

	The following are suggestions for approaching the estimation of large population dynamics.

	\begin{itemize}
		\item Estimate the population state through Random Finite Sets (RFS) and
	apply the models from the previous study. The aim here is to determine a state
	estimation for a swarm of unknown size through a random finite set by solving
	an optimal estimation problem  (typically iterated through a Kalman Filter
	\cite{Doerr2019}. As the swarm is treated probailistically, the theory can
	accomodate an arbitrarily large system. Importantly, this may allow for the
	results from the previous section to be leveraged towards an arbitrary
	population.

	\item Decompose a generic game into a weighted sum of a
	competitive and a cooperative game. Treat these as two separate agents and
	invoke the mean field approximation (MFA) so that any given agent is
	effectively engaged in a three-player game where the strategy of the opponents
	is the average strategy of the population. This leverages the existing results
	on the dynamics of three body problems in game theory \cite{Nagarajan2018} in
	a mixture of co-operative and competitive settings.
	\end{itemize}

	%\textbf{TODO: Elaborate on the technical details of the RFS and three body hypotheses}

@@

    As described in the previous chapter, the control of swarms has been examined through the use of
    mean field models. These models resolve the fact that it is impossible to view the entire system
    as simply the sum of all of the agents and rather model the overall state of the system through
    density functions. Controls are then applied to this function whose evolution is described
    through, typically, one of two partial differential equations: the Fokker-Planck Equation (also
    referred to as the Kolmogorov Forward Equation) and the Vlasov Equation. The former has seen
    some success in recent literature \cite{Elamvazhuthi2019, Li2017,
    Roy2017}, though it makes the assumption that the system evolves through 'drifted
    brownian motion'. This means that the agents are considered to move about independently and
    randomly, though under the influence of a field which affects their velocity. This technique
	has been shown, both theoretically and experimentally, to drive swarm systems in a stable
	manner \cite{Fleig}. The latter is beginning to show promise 
	though control is typically through leadership rather than fields \cite{Burger2019}.

@@

	\begin{itemize}
		\item The stablity of the system: Under what conditions is it possible to drive the
		swarm from one configuration to another in a stable manner? Fortunately, Bellomo et al
		present a candidate lyapunov functional upon which dissipation can be evaluated, though it
		will need to be adapted for the consideration of the consensus models.
		\item The guarantees of the system: Is it possible to ensure that controls remain within an
		admissible set (typically a closed, bounded and convex set \cite{Fredi2010}).
		\item Whether the conservation laws of normalisation and total mass, as presented in 
		\cite{Bellomo2017} can be guaranteed.
	\end{itemize}

@@

	Two proposals for incorporation of social interaction:
	\begin{itemize}
		\item Addition of the agent decisions as a constant in the state $f$. This will require that
		the decisions remain fixed in the state and so it will be required to make sure that the
		controls have no influence on this element.
		\item Weighted summation term in the probability of an agent changing its velocity from
		$v_*$ to
		$v$ due to a field particle with velocity $v^*$ $A[f](v_* \rightarrow v | v_*, v^*)$.
		Here, weights are equal to the agent strategy. This extends to both the swarms in
		which the leaders are making decisions (only leaders have this term) as well as in
		swarms where the population makes decisions (everyone has this term). This will need to be
		done with care though to ensure that normalisation holds. Note that, as this a probabilistic
		approach, we will need to examine the stochastic behaviour of the system and the extent to
		which constraint and conservation satisfaction can be guaranteed.
	\end{itemize}

@@

	%\textbf{TODO: elaborate on the technical details for proposals of social interaction, mention
	%the conservation laws}
